Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of neutron star - black hole binary observations

### 2016-10-17 Paper/paper.tex
compare with Fisher matrix results
moved figure titles to captions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Techniques}\label{s1:techniques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% #################
% THESE FIGURES ARE FOR THE NEXT SECTION
\begin{figure*}
\centering 
\textbf{Illustrative posterior probability distributions for mass-ratio $\eta$,}\par
\textbf{at different SNR values (shown in legend).}\par\medskip
\includegraphics[width=1.8\columnwidth]{plots/SingleSystemEta_q4_0_mc2_25_chi0_50}\\
\caption{We show here probability distributions for mass ratio $\eta$ as measured
for the same signal at different SNRs. The intrinsic parameters of the source
are: $q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$, and $\lambdans=2000$;
and the signal is injected at SNRs $\rho=\{20,30,50\}$ (left to right). The templates
{\it ignore} tidal effects.
% 
In each panel: the dashed red line marks the median value
$\eta^\mathrm{Median}$, while the dashed green line show the true value
$\eta^\mathrm{Injected}$. The darker shading shows
the recovered $90\%$ credible interval for $\eta$, $(\Delta\eta)^{90\%}$.
% 
Comparing systematic and statistical errors, we find that:
at $\rho=20$, $\eta$ measurement is dominated by statistical
errors; at $\rho=30$, the two become comparable; and 
for louder signals ($\rho\simeq50$), the systematic errors dominate.
}
\label{fig:SingleSystemEtaPDFvsSNR}
\end{figure*}
% 
% ###############################
% In this section we summarize various technical aspects of this paper. The model
% used to obtain tidal waveforms is described in Sec.~\ref{s2:waveforms}. The 
% process of inferring source parameters from a GW signal is summarized in 
% Sec.~\ref{s2:bayesian}. The process of generating and combining multiple events
% is instead detailed in the corresponding results section,
% Sec.~\ref{s2:astro_multiple}.

@@

\textbf{Ratio of systematic to statistical errors in measuring $\mchirp$;}\par
\textbf{ignoring tidal effects.}\par\medskip

@@

\caption{We show here the ratio of systematic and statistical

@@

\textbf{Ratio of systematic to statistical errors in measuring $\eta$;}\par
\textbf{ignoring tidal effects.}\par\medskip

@@

\caption{This figure is similar to Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}

@@

\textbf{Ratio of systematic to statistical errors in measuring $\chibh$;}\par
\textbf{ignoring tidal effects.}\par\medskip

@@

\caption{This figure shows the ratio of the systematic and statistical

@@

\textbf{Illustrative posterior probability distributions for NS tidal
deformability $\lambdans$,}\par
\textbf{for signals with different $\lambdans$ values; $\lambdans = 1000,1500,2000,$
from left to right.}\par\medskip

@@

\caption{We show here probability distributions recovered for the NS tidal

@@

\textbf{Statistical uncertainty in $\lambdans$ measurement}\par\medskip

@@

\caption{Here we show the statistical uncertainty in the measurement of

@@

In Fig.~\ref{fig:TT_LambdaCIWidths90_0_Lambda_SNR} we show the main results of
this section. In each panel, as a function of black hole mass and spin, we show
the measured $90\%$ credible interval widths $(\Delta\lambdans)^{90\%}$. These
correspond to the full width of the dark shaded regions in the illustrative
Fig.~\ref{fig:SingleSystemLambdaPDFvsSNR}. The effect of increasing signal
strength can be seen as we go from left to right in each row. The effect of the
NS tidal deformability parameter $\lambdans$ on its own measurability can be
seen by comparing panels within each column, with the NS becoming more
deformable from top to bottom. 
%
A uniform pattern emerges in the left-most column, which corresponds to $\rho=20$.
We find that at this signal strength, our measurement of $\lambdans$ is
dominated by the width of our prior on it. The $90\%$ credible intervals span
the entire allowed range for $\lambdans$, making a reasonable estimation of
$\lambdans$ at $\rho\simeq20$ difficult.
% 
Increasing the signal strength to $\rho=30$ gives marginally better results,
bringing down the statistical uncertainties to within $\pm 75-100\%$ of the
true $\lambdans$ value~\footnote{The symmetric error-bars of $\pm\mathrm{X}\%$
correspond to $\dlambda = 2\mathrm{X}\%$.}.
%
It is not until we reach an SNR as high as $\rho\gtrsim 50$, can we put
meaningful (i.e. $\mathcal{O}(10\%)$) constraints on $\lambdans$. For e.g.,
with a {\it single} observation of a $q=4$ binary with $\chibh\geq 0.6$ and
$\rho = 50$~\footnote{For an optimally oriented source with
$q=4, \mns=1.35M_\odot, \chibh=0.6$, an SNR of $\rho = 50$ corresponds to
a luminosity distance of $\approx 113$Mpc.}, we would be able to estimate 
$\lambdans$ to within $\pm 40\%$ of its true value (which is equivalent to
measuring the ratio of NS radius to mass with an uncertainty of about
$\pm 10\%$).
% 
The results presented so far are in agreement with Sec.~\ref{s1:PEwithnoNS}.

@@

\textbf{Improvement in $\lambdans$ measurement accuracy\\ with multiple observations}\par\medskip

@@

@@

@@

\textbf{No Mass-Gap \hspace{6cm} Mass-Gap}\par\medskip

@@

{\it Top left}: This figure shows the median value of the recovered
probability distribution for $\lambdans$, as a function of the number of events
in the population $N$. There are four ensembles of curves,

@@

{\it Bottom left}: Here we show the interval of $\lambdans$ values within

@@

{\it Right:} These panels are identical to their counterparts on the left,

@@

{\it Left}: This panel shows the width of $\lambdans$ interval within

@@

{\it Right}: This panel shows populations drawn under paradigm B, which

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
We thank Ben Lackey, Francesco Pannarale, Francois Foucart, and Duncan Brown
    for helpful discussions. We gratefully acknowledge support
  for this research at CITA from NSERC of Canada, the Ontario Early 
  Researcher Awards Program, the Canada Research
  Chairs Program, and the Canadian Institute for Advanced Research; at
  Caltech from the Sherman Fairchild Foundation and NSF grants
  PHY-1404569 and AST-1333520; at Cornell from the
  Sherman Fairchild Foundation and NSF grants PHY-1306125 and
  AST-1333129; and at Princeton from NSF grant PHY-1305682 and the
  Simons Foundation.  Calculations were performed at the Vulcan
  supercomputer at the Albert Einstein Institute;
  H.P. and P.K. thank the Albert-Einstein Institute,
  Potsdam, for hospitality during part of the time where this research
  was completed. M.P. thanks CITA for hospitality where part of the work
  was carried out.
\end{acknowledgments}

@@

\section{Statistical uncertainty in measuring non-tidal parameters}\label{as1:nontidalerrors}
% 
% #################
\begin{figure*}
\centering 
\textbf{Statistical measurement uncertainty for NSBH parameters $\mchirp$ (top),
$\eta$ (middle) and $\chibh$ (bottom);\newline ignoring tidal effects.}\par\medskip
\includegraphics[trim = {2cm 0 0 0},width=2.\columnwidth]{plots/TNMchirpCIWidths90_0_Lambda_SNR}\\
\includegraphics[trim = {2cm 0 0 0},width=2.\columnwidth]{plots/TNEtaCIWidths90_0_Lambda_SNR}\\
\includegraphics[trim = {2cm 0 0 0},width=2.\columnwidth]{plots/TNChiBHCIWidths90_0_Lambda_SNR}
\caption{
We show here the statistical uncertainty associated with our measurement of
non-tidal parameters $\mchirp, \eta,$ and $\chibh$ (at $90\%$ credibility),
over the signal parameter space. Individual panels show the same as a function
of BH mass and spin. Across each row, we see the effect of increasing signal
strength (i.e. SNR) with the tidal deformability of the NS $\lambdans$ fixed.
Down each column, we see the effect of increasing $\lambdans$, at fixed SNR.
Tidal effects are ignored in templates.
}
\label{fig:CIWidths90_Lambda_SNR}
\end{figure*}
% #################
%%
In Fig.~\ref{fig:CIWidths90_Lambda_SNR}, we show how {\it precisely} can we
measure non-tidal NSBH parameters $X=\{\mchirp,\eta,\chibh\}$ using BBH templates.
The three panels correspond to $\mchirp$ (top), $\eta$ (middle), and $\chibh$
(bottom), and show the width of these credible intervals $(\Delta X)^{90\%}$
as a function of BH mass/spin (within each sub-panel), and NS properties, i.e.
$\lambdans$ (downwards in each column)~\footnote{We restrict NS mass to
$1.35M_\odot$ and its spin to zero. Varying its tidal deformability $\lambdans$
does not significantly change the measurement uncertainties for non-tidal
binary parameters, as is evident from comparing the two rows in each panel of
Fig.~\ref{fig:CIWidths90_Lambda_SNR}.}.
% 
From the left-most column, we find that: (i) at $\rho=20$ the chirp mass is
measured remarkably well - to a precision of $0.16\%$ of its true value, and
(ii) so is $\chibh$. (iii) The dimensionless mass-ratio $\eta$ is determined
more loosely, with $25+\%$ uncertainty. If the signal is even louder
($\rho\geq 30$), all three measurements gain further precision, especially
$\eta$, for which the relative errors shrink down to single-digit percents.
% % 
We remind ourselves that these results do not tell the full story since the
precision of a measurement is only meaningful if the measurement is accurate 
to begin with. In our case there are tidal effects that have not been
incorporated into our search (BBH) templates, which can lead to a systematic
bias in parameter recovery. We refer the reader to Sec.~\ref{s1:PEwithnoNS} for
a comparative study of both systematic and statistical errors.

\section{Illustrations of Bayesian posteriors}\label{as1:illustrations}
% 
\begin{figure*}
\centering
\textbf{Illustrative posterior probability distributions for NSBH parameters,}\par
\textbf{for signals at different SNR values; $\rho = 20$ (left) and $50$ (right).}\par\medskip
\includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr20}%\\
% \includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr30}%\\
\includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr50}%\\
% \includegraphics[width=0.5\columnwidth]{plots/McEta2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/EtaChiBH2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/McChiBH2D_q4_mc2_25_chi0_50_snr30}\\
% \includegraphics[width=0.5\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}\\
% \includegraphics[width=0.47\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr50}
% \includegraphics[width=0.47\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr50}
% \includegraphics[width=0.47\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr50}
\caption{%
% We illustrate here two-dimensional joint probability distributions, as
% recovered for the intrinsic parameters of a binary with
% $q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$,
% $\lambdans=2000$, and $\rho=30$ (same as in
% Fig.~\ref{fig:SingleSystemLambdaPDFvsSNR}).
% The top row shows the same for combinations of 
% non-tidal parameters, i.e. binary masses and spins, while the middle row 
% shows combinations of $\lambdans$ with non-tidal parameters. The bottom row
% is similar to the middle, with the only difference being that the SNR has been
% turned up to $\rho=50$.
We illustrate here two sets of two-dimensional joint probability distributions,
differing only in signal strength, with $\rho=20$ in the left panel, and
$\rho=50$ in the right. The injected parameters are 
$q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$, and 
$\lambdans=2000$. Contours are shown for $\{1-,2-,3-\}\sigma$ confidence levels.
Templates include tidal effects, as evident in the bottom rows
of both panels which show the correlation of $\lambdans$ with non-tidal 
parameters. Contrasting the two panels illustrates the effect of increasing the
SNR on various parameter measurements.
}
\label{fig:SingleSystemLambda2DPDFs}
\end{figure*}
% #################

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Techniques}\label{s1:techniques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% #################
% THESE FIGURES ARE FOR THE NEXT SECTION
\begin{figure*}
\centering 
% \textbf{Illustrative posterior probability distributions for mass-ratio $\eta$,}\par
% \textbf{at different SNR values (shown in legend).}\par\medskip
\includegraphics[width=1.8\columnwidth]{plots/SingleSystemEta_q4_0_mc2_25_chi0_50}\\
\caption{{\bf Illustrative posterior probability distributions for mass-ratio $\eta$ at different SNR values:}
We show here probability distributions for mass ratio $\eta$ as measured
for the same signal at different SNRs. The intrinsic parameters of the source
are: $q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$, and $\lambdans=2000$;
and the signal is injected at SNRs $\rho=\{20,30,50\}$ (left to right). The templates
{\it ignore} tidal effects.
% 
In each panel: the dashed red line marks the median value
$\eta^\mathrm{Median}$, while the dashed green line show the true value
$\eta^\mathrm{Injected}$. The darker shading shows
the recovered $90\%$ credible interval for $\eta$, $(\Delta\eta)^{90\%}$.
% 
Comparing systematic and statistical errors, we find that:
at $\rho=20$, $\eta$ measurement is dominated by statistical
errors; at $\rho=30$, the two become comparable; and 
for louder signals ($\rho\simeq50$), the systematic errors dominate.
}
\label{fig:SingleSystemEtaPDFvsSNR}
\end{figure*}
% 
% ###############################
% In this section we summarize various technical aspects of this paper. The model
% used to obtain tidal waveforms is described in Sec.~\ref{s2:waveforms}. The 
% process of inferring source parameters from a GW signal is summarized in 
% Sec.~\ref{s2:bayesian}. The process of generating and combining multiple events
% is instead detailed in the corresponding results section,
% Sec.~\ref{s2:astro_multiple}.

@@

% \textbf{Ratio of systematic to statistical errors in measuring $\mchirp$;}\par
% \textbf{ignoring tidal effects.}\par\medskip

@@

\caption{{\bf Ratio of systematic to statistical errors in measuring $\mchirp$, ignoring tidal effects:}
We show here the ratio of systematic and statistical

@@

% \textbf{Ratio of systematic to statistical errors in measuring $\eta$;}\par
% \textbf{ignoring tidal effects.}\par\medskip

@@

\caption{{\bf Ratio of systematic to statistical errors in measuring $\eta$, ignoring tidal effects:}
This figure is similar to Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}

@@

% \textbf{Ratio of systematic to statistical errors in measuring $\chibh$;}\par
% \textbf{ignoring tidal effects.}\par\medskip

@@

\caption{{\bf Ratio of systematic to statistical errors in measuring $\chibh$, ignoring tidal effects:}
This figure shows the ratio of the systematic and statistical

@@

@@

\caption{{\bf Illustrative posterior probability distributions for NS tidal
deformability $\lambdans$:}
We show here probability distributions recovered for the NS tidal

@@

% \textbf{Statistical uncertainty in $\lambdans$ measurement}\par\medskip

@@

\caption{{\bf Statistical uncertainty in $\lambdans$ measurement:}
Here we show the statistical uncertainty in the measurement of

@@

In Fig.~\ref{fig:TT_LambdaCIWidths90_0_Lambda_SNR} we show the main results of
this section. In each panel, as a function of black hole mass and spin, we show
the measured $90\%$ credible interval widths $(\Delta\lambdans)^{90\%}$. These
correspond to the full width of the dark shaded regions in the illustrative
Fig.~\ref{fig:SingleSystemLambdaPDFvsSNR}. The effect of increasing signal
strength can be seen as we go from left to right in each row. The effect of the
NS tidal deformability parameter $\lambdans$ on its own measurability can be
seen by comparing panels within each column, with the NS becoming more
deformable from top to bottom. 
%
A uniform pattern emerges in the left-most column, which corresponds to $\rho=20$.
We find that at this signal strength, our measurement of $\lambdans$ is
dominated by the width of our prior on it. The $90\%$ credible intervals span
the entire allowed range for $\lambdans$, making a reasonable estimation of
$\lambdans$ at $\rho\simeq20$ difficult.
% 
Increasing the signal strength to $\rho=30$ gives marginally better results,
bringing down the statistical uncertainties to within $\pm 75-100\%$ of the
true $\lambdans$ value~\footnote{The symmetric error-bars of $\pm\mathrm{X}\%$
correspond to $\dlambda = 2\mathrm{X}\%$.}.
%
It is not until we reach an SNR as high as $\rho\gtrsim 50$, can we put
meaningful (i.e. $\mathcal{O}(10\%)$) constraints on $\lambdans$. For e.g.,
with a {\it single} observation of a $q=4$ binary with $\chibh\geq 0.6$ and
$\rho = 50$~\footnote{For an optimally oriented source with
$q=4, \mns=1.35M_\odot, \chibh=0.6$, an SNR of $\rho = 50$ corresponds to
a luminosity distance of $\approx 113$Mpc.}, we would be able to estimate 
$\lambdans$ to within $\pm 40\%$ of its true value (which is equivalent to
measuring the ratio of NS radius to mass with an uncertainty of about
$\pm 10\%$).
% 
These results agree well with Sec.~\ref{s1:PEwithnoNS}, and are consistent with
Fisher matrix estimates at high SNRs~\cite{Lackey:2013axa}.

@@

% \textbf{Improvement in $\lambdans$ measurement accuracy\\ with multiple observations}\par\medskip

@@

\caption{{\bf Improvement in $\lambdans$ measurement accuracy with multiple observations:}

@@

\caption{{\bf Improvement in $\lambdans$ measurement accuracy for different NS EoS:}

@@

% \textbf{No Mass-Gap \hspace{6cm} Mass-Gap}\par\medskip

@@

{\bf No Mass-Gap}, {\it top left}: The top figure shows the median value of the recovered
probability distribution for $\lambdans$, as a function of the number of observed 
events $N$. There are four ensembles of curves,

@@

{\bf No Mass-Gap}, {\it bottom left}: Here we show the interval of $\lambdans$ values within

@@

{\bf Mass-Gap}, {\it right column}: These panels are identical to their counterparts on the left,

@@

\caption{{\bf No Mass-Gap} ({\it left}): This panel shows the width of $\lambdans$ interval within

@@

{\bf Mass-Gap} ({\it right}): This panel shows populations drawn under paradigm B, which

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
  We thank Benjamin Lackey, Francesco Pannarale, Francois Foucart, and Duncan Brown
  for helpful discussions. We gratefully acknowledge support
  for this research at CITA from NSERC of Canada, the Ontario Early 
  Researcher Awards Program, the Canada Research
  Chairs Program, and the Canadian Institute for Advanced Research; at
  Caltech from the Sherman Fairchild Foundation and NSF grants
  PHY-1404569 and AST-1333520; at Cornell from the
  Sherman Fairchild Foundation and NSF grants PHY-1306125 and
  AST-1333129; and at Princeton from NSF grant PHY-1305682 and the
  Simons Foundation.  Calculations were performed at the Vulcan
  supercomputer at the Albert Einstein Institute;
  H.P. and P.K. thank the Albert-Einstein Institute,
  Potsdam, for hospitality during part of the time where this research
  was completed. M.P. thanks CITA for hospitality where part of the work
  was carried out.
\end{acknowledgments}

@@

\section{Statistical uncertainty in measuring non-tidal parameters}\label{as1:nontidalerrors}
% 
% #################
\begin{figure*}
\centering 
\includegraphics[trim = {2cm 0 0 0},width=2.\columnwidth]{plots/TNMchirpCIWidths90_0_Lambda_SNR}\\
\includegraphics[trim = {2cm 0 0 0},width=2.\columnwidth]{plots/TNEtaCIWidths90_0_Lambda_SNR}\\
\includegraphics[trim = {2cm 0 0 0},width=2.\columnwidth]{plots/TNChiBHCIWidths90_0_Lambda_SNR}
\caption{{\bf Statistical measurement uncertainty for NSBH parameters,
ignoring tidal effects:}
We show here the statistical uncertainty associated with our measurement of
non-tidal parameters $\mchirp, \eta,$ and $\chibh$ (at $90\%$ credibility),
over the signal parameter space. Individual panels show the same as a function
of BH mass and spin. Across each row, we see the effect of increasing signal
strength (i.e. SNR) with the tidal deformability of the NS $\lambdans$ fixed.
Down each column, we see the effect of increasing $\lambdans$, at fixed SNR.
Tidal effects are ignored in templates.
}
\label{fig:CIWidths90_Lambda_SNR}
\end{figure*}
% #################
%%
In Fig.~\ref{fig:CIWidths90_Lambda_SNR}, we show how {\it precisely} can we
measure non-tidal NSBH parameters $X=\{\mchirp,\eta,\chibh\}$ using BBH templates.
The three panels correspond to $\mchirp$ (top), $\eta$ (middle), and $\chibh$
(bottom), and show the width of these credible intervals $(\Delta X)^{90\%}$
as a function of BH mass/spin (within each sub-panel), and NS properties, i.e.
$\lambdans$ (downwards in each column)~\footnote{We restrict NS mass to
$1.35M_\odot$ and its spin to zero. Varying its tidal deformability $\lambdans$
does not significantly change the measurement uncertainties for non-tidal
binary parameters, as is evident from comparing the two rows in each panel of
Fig.~\ref{fig:CIWidths90_Lambda_SNR}.}.
% 
From the left-most column, we find that: (i) at $\rho=20$ the chirp mass is
measured remarkably well - to a precision of $0.16\%$ of its true value, and
(ii) so is $\chibh$. (iii) The dimensionless mass-ratio $\eta$ is determined
more loosely, with $25+\%$ uncertainty. If the signal is even louder
($\rho\geq 30$), all three measurements gain further precision, especially
$\eta$, for which the relative errors shrink down to single-digit percents.
% % 
We remind ourselves that these results do not tell the full story since the
precision of a measurement is only meaningful if the measurement is accurate 
to begin with. In our case there are tidal effects that have not been
incorporated into our search (BBH) templates, which can lead to a systematic
bias in parameter recovery. We refer the reader to Sec.~\ref{s1:PEwithnoNS} for
a comparative study of both systematic and statistical errors.

\section{Illustrations of Bayesian posteriors}\label{as1:illustrations}
% 
\begin{figure*}
\centering
\includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr20}%\\
% \includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr30}%\\
\includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr50}%\\
% \includegraphics[width=0.5\columnwidth]{plots/McEta2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/EtaChiBH2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/McChiBH2D_q4_mc2_25_chi0_50_snr30}\\
% \includegraphics[width=0.5\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr30}
% \includegraphics[width=0.5\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}\\
% \includegraphics[width=0.47\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr50}
% \includegraphics[width=0.47\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr50}
% \includegraphics[width=0.47\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr50}
\caption{{\bf Illustrative posterior probability distributions for NSBH parameters,
for signals at different SNRs:}
We illustrate here two sets of two-dimensional joint probability distributions,
differing only in signal strength, with $\rho=20$ in the left panel, and
$\rho=50$ in the right. The injected parameters are 
$q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$, and 
$\lambdans=2000$. Contours are shown for $\{1-,2-,3-\}\sigma$ confidence levels.
Templates include tidal effects, as evident in the bottom rows
of both panels which show the correlation of $\lambdans$ with non-tidal 
parameters. Contrasting the two panels illustrates the effect of increasing the
SNR on various parameter measurements.
}
\label{fig:SingleSystemLambda2DPDFs}
\end{figure*}
% #################
